Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-05 WSSSPE3/report/wg_appendix_metrics.tex
Added line breaks. No content change.
editing changes from last 2 weeks - just starting
Section 5.7, Appendix H and I: small changes.

The following summary of the group's discussion represents the Useful Metrics
for Scientific Software working group's discussion during the WSSSPE3 workshop.
The group discussion began by agreeing on the common purpose of creating a set
of guidance giving examples of specific metrics for the success of scientific
software in use, why they were chosen, what they are useful to measure, and any
challenges and pitfalls; then publish this as a white paper. The group discussed
many questions related to useful metrics for scientific software as follows:
\begin{itemize}

@@

\item
However, there is no commonly used standard (DOAP is a good standard but not
widely adopted)

@@

The following opportunities, challenges, and obstacles were discussed:

\begin{itemize}
\item
Metrics are important for:

@@

\item
We don't know if there is a common set of metrics

@@

The following next steps were discussed:

\begin{itemize}
\item
Skype phone call to coordinate shortly after the conclusion of the WSSSPE3 workshop

@@

The following plan for future organization was discussed:

\begin{itemize}
\item
Our group has created a white paper outline with sections assigned to the above
individuals, plus see Section 2 response above for timeline

\item
Organizing coordinating phone calls

>>>>

The following is a summary of the Useful Metrics
for Scientific Software working group's discussion during the WSSSPE3 workshop.
The group discussion began by agreeing on the common purpose of creating a set
of guidance giving examples of specific metrics for the success of scientific
software in use, why they were chosen, what they are useful to measure, and any
challenges and pitfalls; then publish this as a white paper. The group discussed
many questions related to useful metrics for scientific software as follows:
\begin{itemize}

@@

\item
However, there is no commonly-used standard (DOAP is a good standard but not
widely adopted)

@@

The following opportunities, challenges, and obstacles were discussed:
%
\begin{itemize}
\item
Metrics are important for:

@@

\item
We do not know if there is a common set of metrics

@@

The following next steps were discussed:
%
\begin{itemize}
\item
Skype phone call to coordinate shortly after the conclusion of the WSSSPE3 workshop

@@

The following plan for future organization was discussed:
%
\begin{itemize}
\item
Our group has created a white paper outline with sections assigned to the above
individuals; see timeline below. %plus see Section 2 response above for timeline

\item
Organize coordinating phone calls.

### 2016-02-05 WSSSPE3/report/wg_appendix_training.tex
Section 5.7, Appendix H and I: small changes.

While little training focuses specifically on sustainable
software, a variety of training activities increase researcher awareness of
and engagement with software professionals and software engineering practices.
Research Software Engineers are being recognized as critical contributors to
high quality research; the pathway to acquire and master the relevant skills
is not yet clear; equally those skills required by researchers in general are
also not commonly understood nor routinely developed.

@@

While some of this training focuses on applying software engineering practices
within the context of research, meeting the values and goals of research are
less often incorporated as explicit learning outcomes. With software (and
similarly, data) often the only tangible artifact of a research method or
protocol, the dependency between software applications and the quality of
research adds complexity to the learner's journey. In recognition of the longer
term investment required by researchers to integrate such skills into their
research practices, many activities are focusing on emotionally engaging
researchers and cohorts, to build a sense of shared purpose beyond the obvious
goal of technical skill acquisition.

>>>>

While little training focuses specifically on sustainable
software, a variety of training activities increase researcher awareness 
and engagement with software engineering practices and software professionals.
Research Software Engineers are being recognized as critical contributors to
high quality research; the pathway to acquire and master the relevant skills
is not yet clear; equally those skills required by researchers in general are
also not commonly understood nor routinely developed.

@@

While some of this training focuses on applying software engineering practices
within the context of research, meeting the values and goals of research are
less often incorporated as explicit learning outcomes. With software (and
similarly, data) often being the only tangible artifact of a research method or
protocol, the dependency between software applications and the quality of
research adds complexity to the learner's journey. In recognition of the longer
term investment required by researchers to integrate such skills into their
research practices, many activities are focusing on emotionally engaging
researchers and cohorts, to build a sense of shared purpose beyond the obvious
goal of technical skill acquisition.

### 2016-02-05 WSSSPE3/report/wg_main_training.tex
Added line breaks. No content change.
Section 5.7, Appendix H and I: small changes.

\subsubsection{Fit with related activities} Three existing venues for discussion
of related activities are identified:

\begin{itemize}

@@

Next steps have been identified to quickly test whether there is interest in
establishing a community committed to increasing the degree of coordination
across training projects. See Appendix~\ref{sec:appendix_training} for more details about the discussion.

>>>>

\subsubsection{Fit with related activities}

Three existing venues for discussion of related events are
identified:
%
\begin{itemize}

@@

Next steps were identified to quickly test whether there is interest in
establishing a community committed to increasing the degree of coordination
across training projects. See Appendix~\ref{sec:appendix_training} for more
details about the discussion.
